[Artifact Presentation] Damegender: \\ Writing and Comparing Gender Detection Tools

### 2020-05-15 paper2sattose.tex
Beta version2

We would like to thank: Lucía Santamaría and Helena Mihaljevic by the previous work; Daniel Izquierdo and Laura Arjona for starts this research field in the URJC; Jesus González Boticario and the people who work with him at UNED for the motivation towards the machine learning; all people working with Jesus González Barahona and Gregorio Robles.

>>>>

We would like to thank: Lucía Santamaría and Helena Mihaljevic by the previous work; Daniel Izquierdo and Laura Arjona for starting this research field at URJC; Jesus González Boticario and the people who work with him at UNED for the motivation towards the machine learning; all people working with Jesus González Barahona and Gregorio Robles.
